% Appendix grade proof chain for SecureClaw and artifact faithful.
%
% This file is intended to be \input{} from neurips_2025.tex. It is also
% readable standalone as a LaTeX appendix fragment.

\section{Appendix: Proof Chain for Non bypassable Effects and Composition}
\label{app:proofs}

This appendix formalizes SecureClaw's core integrity claim, \emph{no external side effect is
committed without two independently authenticated commit proofs bound to the exact request and hash
context}, and sketches composition with privacy and confinement components.
The formal statements are aligned with the reference implementation and executable validation harnesses.

\paragraph{Scope and assumptions.}
We reason about a PPT adversary that fully controls the untrusted agent runtime and all skill code,
and may send arbitrary requests to the gateway and the executor. The executor's MAC verification keys
are not compromised.
Policy servers are assumed honest for integrity and they compute commit proofs according to the
protocol.
Policy servers are also assumed honest but curious for privacy.
Single server leakage is bounded by an explicit leakage function defined in \texttt{LEAKAGE\_MODEL.md}.

\paragraph{Single proposition.}
The reviewable proposition for this paper is:
no external side effect can be committed without dual valid request bound commit proofs, runtime
plaintext release and patch bypass cannot occur outside explicit interfaces, and cross-principal proof
reuse is rejected by hash-context binding.
In optional SAP mode, a single policy server learns no more than the allowed leakage function under
stated assumptions.
The first clause is formalized by Theorem \ref{thm:nbe}.
The second and third clauses are formalized by Theorems \ref{thm:sm}, \ref{thm:pei}, and \ref{thm:das}.
The optional privacy clause is formalized by Theorem \ref{thm:sap}.

\paragraph{Assumption partition.}
Table \ref{tab:assumption-partition} partitions assumptions by property so that composition dependencies are explicit.

\begin{table}[h]
\centering
\small
\begin{tabular}{lll}
\toprule
Property & Security objective & Main assumptions \\
\midrule
NBE & No unauthorized side effects & MAC EUF-CMA, hash consistency (+hctx), bounded time, replay atomic/persistence assumptions \\
SM & No plaintext flow to runtime & Handle opacity with entropy bound, explicit declassification only \\
PEI & No commit-time patch bypass & Executor sanitize-before-effect semantics, deterministic patch derivation \\
SCS & Skill bypass confinement & Capsule mediation contract and NBE plus SM \\
DAS & No cross-context proof reuse & Delegation signature validity, revocation semantics, hctx hash binding \\
SAP (optional) & Single server transcript privacy & PIR single server security, MPC HBC privacy, non-collusion \\
\bottomrule
\end{tabular}
\caption{Assumption partition for SecureClaw properties.}
\label{tab:assumption-partition}
\end{table}

\subsection{Cryptographic primitives and canonical binding}
\label{app:proofs:primitives}

\paragraph{MAC.}
Let $\mathsf{MAC} = (\mathsf{Tag},\mathsf{Vrfy})$ be a message authentication code with key space
$\mathcal{K}$ and message space $\mathcal{M}$. We assume existential unforgeability under chosen
message attack, abbreviated EUF CMA. The artifact uses HMAC-SHA256:
\[
\mathsf{Tag}_K(m) := \mathrm{HMAC\text{-}SHA256}(K, m), \quad \mathsf{Vrfy}_K(m,t) := [t = \mathsf{Tag}_K(m)].
\]

\paragraph{Canonical serialization and request binding digest.}
Let $\mathsf{Canon}(\cdot)$ be a deterministic canonical JSON serialization implemented in
\texttt{common/canonical.py}. Let
\[
\mathsf{hctx} := (\mathsf{external\_principal},\mathsf{delegation\_jti})
\]
denote the hash context, serialized as a JSON object containing only present fields (empty object if
both are absent). Define the request binding digest:
\[
\mathsf{ReqBind}(\mathsf{intent\_id},\mathsf{caller},\mathsf{session},\mathsf{inputs},\mathsf{hctx}) :=
\left\{
\begin{array}{ll}
\mathrm{HMAC\text{-}SHA256}(k_{\mathsf{bind}},\mathsf{Canon}(\cdot)) & \text{if keyed mode enabled},\\
\mathrm{SHA256}(\mathsf{Canon}(\cdot)) & \text{legacy compatibility mode},
\end{array}
\right.
\]
where $\mathsf{Canon}(\cdot)$ expands to
\[
\mathsf{Canon}\!\left(
\begin{array}{l}
\{\texttt{"v"}:1,\ \texttt{"intent\_id"}:\mathsf{intent\_id},\ \texttt{"caller"}:\mathsf{caller},\ \texttt{"session"}:\mathsf{session},\\
\ \texttt{"inputs"}:\mathsf{inputs},\ \texttt{"context"}:\mathsf{hctx}\}
\end{array}\right).
\]
We assume request-binding security for the configured mode (HMAC PRF-style in keyed mode, SHA-256
collision resistance in legacy mode) and \emph{binding consistency}: both gateway and executor
compute identical byte strings under $\mathsf{Canon}(\cdot)$ for semantically equal JSON objects.
This is an engineering assumption enforced by using the same library routine in both places.

\subsection{Commit proof syntax and executor acceptance predicate}
\label{app:proofs:accept}

Each policy server $\mathcal{P}_\sigma$ for $\sigma\in\{0,1\}$ holds a MAC key $K_\sigma$ and uses a
key identifier field \texttt{kid} for rotation.
Each policy server issues \emph{commit proof shares}. A commit proof share is a pair
$\pi_\sigma = (\mathsf{meta}_\sigma, t_\sigma)$, where:
\begin{align*}
\mathsf{meta}_\sigma := \{&
\texttt{"v"}:1,\ \texttt{"kind"}:\texttt{"commit"},\ \texttt{"server\_id"}:\sigma,\ \texttt{"kid"}:\mathrm{kid},\ \texttt{"ts"}:\tau,\\
&\texttt{"action\_id"}:a,\ \texttt{"program\_id"}:p,\ \texttt{"request\_sha256"}:h,\\
&\texttt{"outputs"}:y_\sigma,\ \texttt{"commit\_tag\_share\_b64"}:\mathrm{tag}_\sigma\},
\end{align*}
and $t_\sigma := \mathsf{Tag}_{K_\sigma}(\mathsf{Canon}(\mathsf{meta}_\sigma))$.
The artifact enforces this format through a machine-checkable commit-evidence schema and
a declarative acceptance-predicate specification used by executable validators.

\paragraph{Executor acceptance.}
Given an effect request $\mathsf{req}$ and two purported commit proof shares $\pi_0,\pi_1$, the
executor $\mathcal{X}$ accepts if and only if the predicate $\mathsf{Accept}(\mathsf{req},\pi_0,\pi_1)$
holds, where:
\begin{enumerate}
\item Both shares parse, have \texttt{v=1} and \texttt{kind="commit"}, and claim distinct
\texttt{server\_id} values in $\{0,1\}$.
\item MAC verification succeeds:
$\mathsf{Vrfy}_{K_\sigma}(\mathsf{Canon}(\mathsf{meta}_\sigma), t_\sigma)=1$ for $\sigma\in\{0,1\}$,
using the key for the claimed \texttt{kid}.
\item Freshness: $\lvert \mathrm{now} - \tau\rvert \leq \mathrm{TTL}_{\mathsf{mac}}$
where $\mathrm{TTL}_{\mathsf{mac}}$ is configured by the environment variable \texttt{POLICY\_MAC\_TTL\_S}.
\item Context agreement: both shares bind the same $(a,p,h)$ tuple.
\item Request binding: letting $(\mathsf{intent\_id},\mathsf{caller},\mathsf{session},\mathsf{inputs},\mathsf{hctx})$
be the effectful fields of $\mathsf{req}$, we require $h =
\mathsf{ReqBind}(\mathsf{intent\_id},\mathsf{caller},\mathsf{session},\mathsf{inputs},\mathsf{hctx})$.
\item Replay protection: the action identifier $a$ has not been accepted before within the replay
window. The artifact uses \texttt{\_ReplayGuard.check\_and\_mark}.
\item Policy bits reconstructed from $(y_0,y_1)$ indicate allow; if a confirmation bit is set then
the request includes explicit user confirmation; and any sanitize patch is applied.
\end{enumerate}

For freshness soundness we model bounded clock skew and bounded transport delay: if a share is minted
at honest time $t$, executor acceptance is evaluated at time $t'$ with
$|t'-t|\leq \Delta_{\mathsf{clk}}+\Delta_{\mathsf{net}}$, and we require
$\Delta_{\mathsf{clk}}+\Delta_{\mathsf{net}}<\mathrm{TTL}_{\mathsf{mac}}$.

\subsection{Security game for non bypassable effects}
\label{app:proofs:nbe-game}

We formalize \emph{non bypassable effects} as an integrity game where the adversary controls the
untrusted runtime and can obtain valid commit proofs for adaptively chosen preview tuples, but must
not be able to commit an effect outside the authorized set.

\paragraph{Oracles.}
The challenger provides a \emph{commit oracle} $\mathcal{O}_{\mathsf{commit}}(\rho)$ that, on input
$\rho = (\mathsf{intent\_id},\mathsf{caller},\mathsf{session},\mathsf{inputs},\mathsf{hctx})$, returns a fresh
action id $a$ and valid proof shares $(\pi_0,\pi_1)$ whose \texttt{request\_sha256} equals
$\mathsf{ReqHash}(\rho)$. The challenger records the authorized binding tuple
$(a,p,\mathsf{ReqHash}(\rho),\rho)$ in a set $\mathcal{S}$.

\paragraph{Experiment $\mathsf{Exp}^{\mathsf{NBE}}(\lambda)$.}
\begin{enumerate}
\item The challenger samples independent MAC keys $K_0,K_1 \leftarrow \mathcal{K}$ and initializes
replay state empty.
\item The adversary $\mathcal{A}$ may adaptively query $\mathcal{O}_{\mathsf{commit}}(\rho)$.
\item $\mathcal{A}$ outputs an effect request $\mathsf{req}^\star$ and two shares
$(\pi_0^\star,\pi_1^\star)$.
\item $\mathcal{A}$ wins if $\mathsf{Accept}(\mathsf{req}^\star,\pi_0^\star,\pi_1^\star)=1$ and at
least one of the following holds:
\begin{enumerate}
\item \textbf{No-auth:} the accepted $(a^\star,p^\star,h^\star)$ tuple is not in $\mathcal{S}$.
\item \textbf{Binding break:} $(a^\star,p^\star,h^\star)$ is in $\mathcal{S}$, but the request
tuple $\rho(\mathsf{req}^\star)$ differs from the $\rho$ recorded for that context.
\item \textbf{Replay:} the executor accepts the same $a^\star$ twice within the replay window.
\end{enumerate}
\end{enumerate}

\subsection{Main theorem: no side effects without dual proofs}
\label{app:proofs:nbe-thm}

\begin{theorem}[No side effects without dual commit proofs]\label{thm:nbe}
Assume (i) $\mathsf{MAC}$ is EUF-CMA secure; (ii) SHA-256 is collision resistant and
$\mathsf{Canon}(\cdot)$ is consistent; (iii) the executor enforces $\mathsf{Accept}$ as specified;
(iv) bounded time drift/latency satisfies
$\Delta_{\mathsf{clk}}+\Delta_{\mathsf{net}}<\mathrm{TTL}_{\mathsf{mac}}$; (v) replay
check-and-mark is atomic for each action id and replay state durability assumptions hold for the
configured replay window. Then for any PPT adversary
$\mathcal{A}$ there exist PPT reductions $\mathcal{B}_0,\mathcal{B}_1,\mathcal{C}$ such that:
\[
\Pr[\mathsf{Exp}^{\mathsf{NBE}}(\lambda)=1]
\le \mathrm{Adv}^{\mathrm{euf\text{-}cma}}_{\mathsf{MAC}}(\mathcal{B}_0)
 + \mathrm{Adv}^{\mathrm{euf\text{-}cma}}_{\mathsf{MAC}}(\mathcal{B}_1)
 + \mathrm{Adv}^{\mathrm{coll}}_{\mathrm{SHA256}}(\mathcal{C})
 + \varepsilon_{\mathrm{time}}(\lambda)
 + \varepsilon_{\mathrm{replay\_atomic}}(\lambda)
 + \varepsilon_{\mathrm{replay\_persist}}(\lambda),
\]
where $\varepsilon_{\mathrm{time}}$ captures only violations of the time-drift/latency assumption,
$\varepsilon_{\mathrm{replay\_atomic}}$ captures failures of atomic check-and-mark semantics, and
$\varepsilon_{\mathrm{replay\_persist}}$ captures replay-state durability violations (for example
restart/fallback configurations outside the claimed durable window).
\end{theorem}

\paragraph{Proof (reduction by cases).}
Fix an adversary $\mathcal{A}$ that wins the experiment and consider the accepting transcript
$(\mathsf{req}^\star,\pi_0^\star,\pi_1^\star)$.
By acceptance, both MACs verify and both meta records bind the same context
$(a^\star,p^\star,h^\star)$ with fresh timestamps, and $h^\star$ equals the executor's recomputed
$\mathsf{ReqHash}(\rho(\mathsf{req}^\star))$.

\emph{Case 1 (No-auth).} Suppose $(a^\star,p^\star,h^\star)\not\in\mathcal{S}$. The challenger never
queried its own commit oracle on the message $\mathsf{Canon}(\mathsf{meta}_0^\star)$ or
$\mathsf{Canon}(\mathsf{meta}_1^\star)$ for this context. Since both tags verify, at least one share
is a fresh valid tag on a message not previously tagged under the corresponding key. We build a UF-CMA
forger $\mathcal{B}_0$ (symmetrically $\mathcal{B}_1$) that embeds its UF-CMA challenge key as $K_0$,
answers $\mathcal{O}_{\mathsf{commit}}$ by querying its signing oracle for $\mathsf{Canon}(\mathsf{meta}_0)$,
and outputs $(\mathsf{Canon}(\mathsf{meta}_0^\star),t_0^\star)$ when $\mathcal{A}$ wins in this case.

\emph{Case 2 (Binding break).} Suppose $(a^\star,p^\star,h^\star)\in\mathcal{S}$, but
$\rho(\mathsf{req}^\star)\neq \rho$ recorded for that context. Acceptance implies:
\[
h^\star = \mathsf{ReqHash}(\rho(\mathsf{req}^\star)) = \mathsf{ReqHash}(\rho).
\]
If $\rho(\mathsf{req}^\star)\neq \rho$ then we have found a collision in SHA-256 \emph{under the
canonical encoding} (or an inconsistency in $\mathsf{Canon}$). A reduction $\mathcal{C}$ outputs the
two distinct canonical inputs whose hashes are equal. This contradicts collision resistance or the
engineering consistency assumption.

\emph{Case 3 (Replay).} If the executor accepts a previously accepted $a^\star$ within the replay
window, then the replay guard's check-and-mark failed due to loss/corruption of replay state or lack
of atomicity. This is outside the cryptographic model and is captured by
$\varepsilon_{\mathrm{replay\_atomic}}+\varepsilon_{\mathrm{replay\_persist}}$.

\emph{Case 4 (Time-bound assumption failure).} If acceptance occurs outside the intended operational
freshness envelope due to unmodeled clock drift or transport delay violations, this contributes only
to $\varepsilon_{\mathrm{time}}$.

Taking a union bound over the cases yields the theorem.
\qed

\subsection{Session, caller, TTL binding}
\label{app:proofs:binding}

Theorem~\ref{thm:nbe} already incorporates binding of $\mathsf{caller}$ and $\mathsf{session}$ because
they are included in $\mathsf{ReqHash}$ together with $\mathsf{hctx}$.
Freshness (TTL) is enforced by the executor's timestamp check under the stated
$\Delta_{\mathsf{clk}},\Delta_{\mathsf{net}}$ assumption.
Thus, any attempt to reuse a commit proof for a different caller, session, hash-context binding, or
effectful input must either fail MAC verification/binding checks or imply a hash collision.
Replay claims across restarts additionally require either persistent replay state
(\texttt{EXECUTOR\_REPLAY\_DB\_PATH}) or an explicit no-restart assumption over the replay window.

\subsection{Composition with privacy and confinement}
\label{app:proofs:composition}

We state a composition theorem that makes the conjunction of properties explicit.
For mechanized consistency, the artifact includes an explicit state model checker
\texttt{formal/secureclaw\_model\_check.py} that enumerates bounded adversary behaviors under idealized
cryptography and checks bounded consistency for NBE, SM, PEI, DAS, and SCS shape assumptions when the
executor enforces $\mathsf{Accept}$ and the interface fields match the schema.

\paragraph{Dependency decomposition.}
The combined argument separates responsibilities at interface boundaries.
PIR and two party computation are used only for transcript privacy and do not enforce side effects.
Executor acceptance and replay logic enforce effect integrity.
Gateway handleization enforces runtime plaintext confinement.
Capsule mediation enforces skill process and network confinement.
This partition prevents hidden circular assumptions in the composition theorem.

\paragraph{Combined experiment.}
Define a combined experiment $\mathsf{Exp}^{\mathsf{SC}}(\lambda)$ for SecureClaw.
The adversary controls the untrusted runtime and all skills and may send arbitrary requests to the
gateway and the executor.
The adversary may also corrupt at most one policy server and obtain its full internal view.
The experiment outputs $1$ if any of the following bad events occurs.

\begin{itemize}
\item $\mathsf{Bad}_{\mathsf{NBE}}$: an external side effect is committed without two valid commit proofs
bound to the exact request hash, within the freshness window, and not replayed.
\item $\mathsf{Bad}_{\mathsf{SM}}$: the adversary learns a sensitive plaintext value that is not in the
explicit declassification leakage $L_{\mathsf{SM}}$.
\item $\mathsf{Bad}_{\mathsf{PEI}}$: the executor accepts an effect commit where a required sanitize patch
was not applied to the committed payload.
\item $\mathsf{Bad}_{\mathsf{SCS}}$: while the capsule mediation contract holds, the adversary performs a
forbidden direct action that bypasses the gateway and executor.
\item $\mathsf{Bad}_{\mathsf{DAS}}$: commit evidence minted for one $(\mathsf{caller},\mathsf{session},\mathsf{hctx})$
is accepted under a different binding context.
\item $\mathsf{Bad}_{\mathsf{SAP}}$: the adversary distinguishes two action sequences with equal leakage
under $L_{\mathsf{policy}}$ by observing the full transcript view of one policy server (optional mode).
\end{itemize}

\begin{theorem}[Composition of SecureClaw properties]\label{thm:composition}
Assume the conditions of Theorems \ref{thm:nbe}, \ref{thm:sm}, \ref{thm:pei}, \ref{thm:scs}, and \ref{thm:das}.
If SAP mode is claimed, additionally assume Theorem \ref{thm:sap}.
Then for any probabilistic polynomial time adversary $\mathcal{A}$ the winning probability in the
combined experiment satisfies
\[
\Pr[\mathsf{Exp}^{\mathsf{SC}}(\lambda)=1]
\le
\Pr[\mathsf{Bad}_{\mathsf{NBE}}]
\;+\;
\Pr[\mathsf{Bad}_{\mathsf{SM}}]
\;+\;
\Pr[\mathsf{Bad}_{\mathsf{PEI}}]
\;+\;
\Pr[\mathsf{Bad}_{\mathsf{SCS}}]
\;+\;
\Pr[\mathsf{Bad}_{\mathsf{DAS}}]
\;+\;
\Pr[\mathsf{Bad}_{\mathsf{SAP}}].
\]
Moreover, each term is negligible in $\lambda$ under the corresponding theorem assumptions.
\end{theorem}

\paragraph{Proof.}
The combined experiment outputs $1$ if and only if at least one bad event occurs.
By the union bound,
\[
\Pr[\mathsf{Bad}_{\mathsf{NBE}} \lor \mathsf{Bad}_{\mathsf{SM}} \lor \mathsf{Bad}_{\mathsf{PEI}} \lor \mathsf{Bad}_{\mathsf{SCS}} \lor \mathsf{Bad}_{\mathsf{DAS}} \lor \mathsf{Bad}_{\mathsf{SAP}}]
\le
\Pr[\mathsf{Bad}_{\mathsf{NBE}}] + \Pr[\mathsf{Bad}_{\mathsf{SM}}] + \Pr[\mathsf{Bad}_{\mathsf{PEI}}] + \Pr[\mathsf{Bad}_{\mathsf{SCS}}] + \Pr[\mathsf{Bad}_{\mathsf{DAS}}] + \Pr[\mathsf{Bad}_{\mathsf{SAP}}].
\]
No disjointness assumption is required for this step; event overlap only affects bound tightness.
Theorem \ref{thm:nbe} bounds $\Pr[\mathsf{Bad}_{\mathsf{NBE}}]$ by MAC unforgeability, hash collision
resistance, bounded time assumptions, and replay-store atomicity/durability assumptions.
Theorem \ref{thm:sm} bounds $\Pr[\mathsf{Bad}_{\mathsf{SM}}]$ by the handleization and declassification
assumptions.
Theorem \ref{thm:pei} bounds $\Pr[\mathsf{Bad}_{\mathsf{PEI}}]$ by executor patch-application soundness.
Theorem \ref{thm:das} bounds $\Pr[\mathsf{Bad}_{\mathsf{DAS}}]$ by delegation verification and hash-context binding.
Theorem \ref{thm:sap} bounds $\Pr[\mathsf{Bad}_{\mathsf{SAP}}]$ by PIR and two party computation
security up to the stated leakage.
Theorem \ref{thm:scs} bounds $\Pr[\mathsf{Bad}_{\mathsf{SCS}}]$ by the capsule mediation contract and
the integrity and confidentiality properties of the gateway and executor path.
\qed

\subsection{Capsule mediation contract as a system assumption}
\label{app:proofs:mc}

We define the capsule mediation contract as an explicit system assumption that can be validated by
platform specific configurations and tests.

\paragraph{Contract definition.}
Let $MC$ be a predicate over the runtime environment and its execution.
The contract requires the following properties.

\begin{itemize}
\item Filesystem confinement. The runtime can read only its code and a dedicated workspace directory.
The runtime cannot read host secret paths such as SSH keys or application credential stores.
\item Network confinement. The runtime cannot initiate public network connections.
If a network stack is used for transport then only the gateway address is reachable.
\item Process confinement. The runtime cannot spawn arbitrary processes.
Only a fixed allowlist required for the runtime operation is permitted.
\item Transport confinement. The runtime can reach the gateway only through a single constrained
transport endpoint, preferably a Unix domain socket.
\end{itemize}

\paragraph{Cross platform minimal realizations.}
The artifact provides a macOS capsule policy using \texttt{sandbox-exec} with profile
\texttt{capsule/capsule.sb}, and a Linux capsule policy using \texttt{bubblewrap} with a network
namespace in \texttt{capsule/run\_smoke\_linux.sh}.
Both realizations use a constrained gateway transport and are exercised by the same smoke test logic
in \texttt{capsule/smoke.py}.

\paragraph{Testable assertions.}
The smoke test asserts that direct reads of a host secret path fail, that direct public network
requests fail, that direct HTTP posts to a local exfiltration endpoint fail when the capsule is
configured for a netless transport, that direct process execution is denied in the macOS capsule
configuration, and that a gateway action request succeeds through the constrained transport.
These assertions are recorded as a structured JSON report.

\subsection{Executable validation of the acceptance predicate}
\label{app:proofs:executable}

Theorem \ref{thm:nbe} is a cryptographic statement about any adversary in the model.
The artifact also provides an executable specification that checks the concrete acceptance predicate.

\paragraph{Validation statement.}
Let $\mathsf{Accept}$ be the acceptance predicate specified in Section \ref{app:proofs:accept}.
The artifact provides:
\begin{itemize}
\item unit-level checks that assert accept/reject behavior under mutated evidence;
\item an end-to-end harness that exercises gateway, policy servers, and executor against adversarial request mutations.
\end{itemize}
The harness checks rejection under replay, session mismatch, caller mismatch, missing proof share,
MAC mutation, request hash mutation, action identifier mutation, and timestamp expiration.
These checks provide code level evidence that the artifact enforces the exact acceptance predicate
assumed by the reduction in Theorem \ref{thm:nbe}.

\subsection{Secret myopia game and theorem}
\label{app:proofs:sm}

We formalize secret myopia as a simulation based confidentiality property for the untrusted runtime.
The definition is implementation oriented.
It treats the gateway and executor as trusted and asserts that sensitive plaintext does not flow to
the untrusted runtime except through an explicit declassification interface.

\paragraph{Leakage function for SM.}
Let $L_{\mathsf{SM}}$ include:
handle identifiers,
handle labels,
handle time to live values,
policy decision bits,
sanitization patch identifiers,
and any explicitly declassified outputs that follow user confirmation.
It excludes any other function of sensitive plaintext stored inside the gateway.

\paragraph{Experiment $\mathsf{Exp}^{\mathsf{SM}}(\lambda)$.}
The challenger initializes the gateway and gives the adversary control of the untrusted runtime.
The adversary interacts with the gateway by issuing arbitrary action requests and receiving gateway
responses.
The adversary wins if it outputs a bit indicating which of two challenger chosen secret values was
stored in a handle, with advantage non negligible over one half, without an allowed declassification
event that reveals that value.

\paragraph{Theorem.}
\begin{theorem}[Secret myopia by handleization]\label{thm:sm}
Assume the gateway never returns sensitive plaintext to the untrusted runtime except through an
explicit declassification interface that requires confirmation and includes declassified content in
$L_{\mathsf{SM}}$.
Assume handle identifiers are sampled independently of plaintext with at least 128 bits of entropy
(artifact default: \texttt{secrets.token\_urlsafe(16)}), so any adversary making at most $q_h$
online handle guesses in the valid window has success probability at most $q_h/2^{128}$.
Then the system satisfies secret myopia with leakage $L_{\mathsf{SM}}$ up to additive
$q_h/2^{128}$ and explicit declassification leakage.
\end{theorem}

\paragraph{Proof.}
We construct a simulator $\mathcal{S}$ that, given $L_{\mathsf{SM}}$, produces a distribution
indistinguishable from the view of the adversary.
Whenever the real gateway would mint a handle bound to some plaintext, $\mathcal{S}$ instead mints a
fresh random handle identifier and records only the public metadata required by $L_{\mathsf{SM}}$.
All subsequent uses of that handle by the adversary are simulated by lookup on the simulator side.
Because handle identifiers are sampled independently of plaintext and the adversary never receives
plaintext unless it appears in the leakage, the simulated responses match the real responses
distribution up to handle guessing probability $q_h/2^{128}$ and the declassified outputs already
included in $L_{\mathsf{SM}}$.
Therefore any additional adversary advantage implies either a violation of the stated handle-entropy
assumption or a direct plaintext flow outside the declassification interface, which contradicts the
premise.
\qed

\paragraph{Executable evidence.}
The artifact includes unit tests for handleization and declassification semantics across tool,
inter-agent, and memory surfaces.

\subsection{Patch-carrying egress integrity theorem}
\label{app:proofs:pei}

\paragraph{Experiment $\mathsf{Exp}^{\mathsf{PEI}}(\lambda)$.}
The adversary outputs a commit request and dual proof shares.
The adversary wins if executor acceptance succeeds but the committed effect payload does not match the
payload obtained by applying the required sanitize patch encoded by policy outputs.

\paragraph{Theorem.}
\begin{theorem}[Patch-carrying egress integrity]\label{thm:pei}
Assume the executor acceptance predicate is implemented as specified and all effect sinks execute only
after executor-side sanitize application when policy requires patching.
Then $\Pr[\mathsf{Bad}_{\mathsf{PEI}}]$ is bounded by implementation-spec divergence probability plus
negligible cryptographic failure terms inherited from Theorem \ref{thm:nbe}.
\end{theorem}

\paragraph{Proof sketch.}
If acceptance succeeds, the executor has reconstructed policy bits and must apply required patch
constraints before effect execution.
Therefore any accepted unsanitized commit implies either a direct violation of executor implementation
logic or a mismatch between implementation and declared acceptance semantics.
\qed

\subsection{Single auditor privacy game and theorem}
\label{app:proofs:sap}

We formalize single auditor privacy as transcript indistinguishability for a single policy server,
parameterized by an explicit leakage function.
The leakage function is defined in Appendix \ref{app:leakage}.

\paragraph{Experiment $\mathsf{Exp}^{\mathsf{SAP}}(\lambda)$.}
The adversary outputs two action sequences $W_0$ and $W_1$ such that
$L_{\mathsf{policy}}(W_0) = L_{\mathsf{policy}}(W_1)$.
The challenger samples a bit $b$ and executes the system on $W_b$.
The challenger then reveals the full transcript view $\mathsf{View}(\mathcal{P}_\sigma)$ for one
policy server $\mathcal{P}_\sigma$.
The adversary outputs a guess $b'$.

\paragraph{Lemma 1 (PIR-view simulation).}
For fixed $\sigma \in \{0,1\}$, under single-server security of the DPF/FSS PIR scheme, there exists
a PPT simulator $\mathsf{Sim}^{\mathsf{PIR}}_\sigma$ such that the PIR transcript fragment visible to
$\mathcal{P}_\sigma$ is computationally indistinguishable from
$\mathsf{Sim}^{\mathsf{PIR}}_\sigma(L_{\mathsf{PIR}})$.

\paragraph{Lemma 2 (MPC-view simulation).}
Under honest-but-curious security of the two-party MPC protocol, there exists a PPT simulator
$\mathsf{Sim}^{\mathsf{MPC}}_\sigma$ such that the MPC transcript fragment visible to
$\mathcal{P}_\sigma$ is computationally indistinguishable from
$\mathsf{Sim}^{\mathsf{MPC}}_\sigma(L_{\mathsf{MPC}})$.

\paragraph{Lemma 3 (Deterministic fixed-shape composition).}
Assume the gateway scheduler is fixed-shape for covered intents: endpoint class, program id, batch
geometry, and timing bucket policy are deterministic functions of
$L_{\mathsf{CONFIRM}}$ and $L_{\mathsf{TIME}}$.
Then non-cryptographic transcript components are exactly computable from
$(L_{\mathsf{CONFIRM}},L_{\mathsf{TIME}})$.

\paragraph{Theorem.}
\begin{theorem}[Single-auditor transcript privacy under PIR+MPC]\label{thm:sap}
Assume:
\begin{enumerate}
\item DPF/FSS two-server PIR is secure against one server (single key-share view),
\item the fixed policy MPC is secure in the honest-but-curious model,
\item policy servers do not collude, and
\item deployment enforces fixed-shape routing/scheduling consistent with
$L_{\mathsf{policy}}=(L_{\mathsf{PIR}},L_{\mathsf{MPC}},L_{\mathsf{CONFIRM}},L_{\mathsf{TIME}})$.
\end{enumerate}
Then for each $\sigma \in \{0,1\}$ there exists a PPT simulator $\mathsf{Sim}_\sigma$ such that for
all PPT distinguishers $D$,
\[
\bigl|\Pr[D(\mathsf{View}(\mathcal{P}_\sigma))=1] - \Pr[D(\mathsf{Sim}_\sigma(L_{\mathsf{policy}}))=1]\bigr|
\]
is negligible in $\lambda$.
\end{theorem}

\paragraph{Proof.}
Fix $\sigma$ and define hybrids.
$H_0$ is the real single-server transcript.
$H_1$ replaces PIR-visible fragments using $\mathsf{Sim}^{\mathsf{PIR}}_\sigma$; by Lemma 1,
$H_0 \approx_c H_1$.
$H_2$ additionally replaces MPC-visible fragments using $\mathsf{Sim}^{\mathsf{MPC}}_\sigma$; by
Lemma 2, $H_1 \approx_c H_2$.
By Lemma 3, all remaining scheduler/confirmation/timing metadata in $H_2$ is computable from
$(L_{\mathsf{CONFIRM}},L_{\mathsf{TIME}})$, hence from $L_{\mathsf{policy}}$.
Therefore $H_2$ is exactly (or efficiently) sampleable by a simulator
$\mathsf{Sim}_\sigma(L_{\mathsf{policy}})$.
Triangle inequality over hybrid distances gives negligible distinguishing advantage, proving the
theorem.
\qed

\paragraph{Executable evidence.}
The artifact includes fixed-shape mixing and padding logic for PIR and unified policy routing,
plus end-to-end distinguishability sweeps that measure residual transcript signal under ablations.

\subsection{Skill confined safety game and theorem}
\label{app:proofs:scs}

Skill confined safety is a conditional property.
It relies on a capsule mediation contract that constrains the untrusted runtime environment.
The contract is specified in Section \ref{sec:limits}.

\paragraph{Experiment $\mathsf{Exp}^{\mathsf{SCS}}(\lambda)$.}
The adversary controls the skill code and attempts to perform one of the following forbidden direct
actions without using the gateway and executor path:
host secret reads, public network exfiltration, or arbitrary process execution.
The adversary wins if it succeeds while the capsule mediation contract holds.

\paragraph{Theorem.}
\begin{theorem}[Skill confined safety under a capsule mediation contract]\label{thm:scs}
Assume the capsule mediation contract holds and prevents the forbidden direct actions.
Assume non bypassable effects and secret myopia hold for the gateway and executor path.
Then the system satisfies skill confined safety.
\end{theorem}

\paragraph{Proof.}
By the capsule mediation contract, any forbidden direct action attempt that does not traverse the
gateway fails and cannot reach an external sink.
Therefore any external side effect must traverse the executor, which enforces non bypassable effects.
Any attempted exfiltration of sensitive plaintext through allowed interfaces is prevented by secret
myopia unless the user explicitly declassifies it, in which case the leakage is intentional and
auditable.
Thus the adversary cannot perform forbidden direct actions or unauthorized effects under the stated
assumptions.
\qed

\paragraph{Executable evidence.}
The artifact provides a capsule smoke test that attempts direct filesystem reads, direct network
access, and direct process execution from within the capsule boundary and asserts denial.
\subsection{Delegation-aware binding safety theorem}
\label{app:proofs:das}

\paragraph{Experiment $\mathsf{Exp}^{\mathsf{DAS}}(\lambda)$.}
The adversary first obtains valid PREVIEW evidence for one binding context
$(\mathsf{caller},\mathsf{session},\mathsf{hctx})$ and then attempts COMMIT under a different context
by swapping caller, session, external principal, or delegation identifier.
The adversary wins if executor acceptance succeeds under the mismatched binding.

\paragraph{Theorem.}
\begin{theorem}[Delegation-aware hash-context binding safety]\label{thm:das}
Assume delegation signatures are unforgeable, revocation checks are sound, canonicalization is
consistent, and executor recomputes request binding digest including $\mathsf{hctx}$.
Then successful cross-context replay implies either MAC/hash break events already covered by
Theorem \ref{thm:nbe} or signature/revocation assumption failure, hence
$\Pr[\mathsf{Bad}_{\mathsf{DAS}}]$ is negligible under these assumptions.
\end{theorem}

\paragraph{Proof sketch.}
Changing caller, session, or hash-context changes the bound request digest.
Executor acceptance requires equality between recomputed hash and proof hash, so mismatched-context
reuse fails unless cryptographic binding assumptions are violated.
\qed
